
\documentclass[msc,ai,logo,sansheadings]{infthesis}
\shieldtype{3}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{listings}
\usepackage[english]{babel}

\title{\bigskip \bigskip \bigskip \bigskip \bigskip \bigskip \bigskip Paraphrasing In Context Of \\ Computer Aided Translation}
\author{Turan Rustamli}

\abstract{%
	\begin{flushleft}
    We developed a novel paraphrasing service which is provided within a Computer Aided Translation tool. Our service aims to help human translators to fix automatic translations by suggesting paraphrases to any parts of the translation that they specify. 
	\end{flushleft}

	\begin{flushleft}
    The originality of our paraphrasing approach is that it uses the search graph data, produced during the machine translation process, as the main data source. To test feasibility of our method we carried out two major evaluation stages. During the first stage we designed an original automatic paraphrasing evaluation tool and used it to assess ten different versions of our paraphrasing approach. In order to support our findings we carried out the second stage, during which a group of four annotators judged paraphrasing results produced by our service. The results of the both stages demonstrate that the information available from the search graph is sufficient to produce useful paraphrasing suggestions.
	\end{flushleft}

	\begin{flushleft}
    Taking advantage of the interactivity of the Computer Aided Translation process, we also implemented a novel feature that lets the paraphrasing service to provide improved results by utilising feedback from a user.
	\end{flushleft}
}

\begin{document}

\begin{preliminary}

\maketitle

\begin{acknowledgements}
\begin{large}
Many thanks to my supervisor Prof. Philipp Koehn for his direction and advice throughout the dissertation. I also wish to express my gratitude to the Government of Azerbaijan Republic for funding my MSc degree through the ``State Scholarship Program on Education of Azerbaijani Youth Abroad''.
\end{large}
\end{acknowledgements}

\standarddeclaration

%% \dedication{To my mummy.}

\tableofcontents

% \listoffigures
% \listoftables

\end{preliminary}

%%%%%%%%
%% Include your chapter files here. See the sample chapter file for the basic
%% format.

\input{chap1}
\input{chap2}
\input{chap3}
\input{chap4}
\input{chap5}
\input{chap6}
%% ... etc ...

%%%%%%%%
%% Any appendices should go here. The appendix files should look just like the
%% chapter files.
\appendix
\include{appendix1}
%% ... etc...


\bibliographystyle{apalike}
% \singlespace

\bibliography{library}

\end{document}
